\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses with Citizen Science

### 2015-05-10 doc/sw-system.tex
Reading through, up to Results section.

How should we model these compressed data? The circumstances of each
classification are quite complex, as are the human classifiers in general: the
volunteers learn more about the problem as they go, but also inevitably make
occasional mistakes (especially when classifying at high speed).
To cope with this uncertainty, we assign a
simple software {\it agent} to partner each volunteer. The agent's task is to
interpret their volunteer's classification data as best it can, using a model
that makes a number of necessary approximations. These interpretations will
then include uncertainty arising as a result of the volunteer's efforts and
also the agent's approximations.
The agent will be able to predict, using its model, the probability of a test
subject being a $\LENS$ given both its volunteer's classification and its
volunteer's past experience. In this section we describe how these agents work,
and other aspects of the \SW analysis pipeline (SWAP).

@@

When all the subjects had either been retired, or classified around 10 times or
more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification number
of 50 each. The number of subjects at \StageTwo was small enough that we did not
need to retire any: instead, we simply collected classifications for a fixed
period of time (about 4 weeks). Without the time pressure motivating an
online-only calculation (as there had been during \StageOne), we carried out an
offline analysis (\Sref{sec:swap:offline} above) of the  \StageTwo
classifications as well, both  for comparison and as we will see in the next
section, to improve the pipeline performance.

>>>>

How should we model these compressed data? The circumstances of each
classification are quite complex, as are the human classifiers themselves: the
volunteers learn more about the problem as they go, but also inevitably make
occasional mistakes (especially when classifying at high speed).
To cope with this uncertainty, we assign a
simple software {\it agent} to partner each volunteer. The agent's task is to
interpret their volunteer's classification data as best it can, using a model
that makes a number of necessary approximations. These interpretations will
then include uncertainty arising as a result of the volunteer's efforts and
also the agent's approximations.
The agent will be able to predict, using its model, the probability of a test
subject being a $\LENS$ given both its volunteer's classification and its
volunteer's past experience. In this section we describe how these agents work,
and other aspects of the \SW analysis pipeline (SWAP).

@@

When all the subjects had either been retired, or at least
classified around 10 times or
more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification number
of 50 each. The number of subjects at \StageTwo was small enough that we did not
need to retire any: instead, we simply collected classifications for a fixed
period of time (about 4 weeks). Without the time pressure motivating an
online-only calculation (as there had been during \StageOne), we carried out an
offline analysis (\Sref{sec:swap:offline} above) of the  \StageTwo
classifications as well, both  for comparison and as we will see in the next
section, to improve the pipeline performance.
